\documentclass[]{chowes-resume}


\begin{document}
\thispagestyle{empty}


\namesection{Colin}{Howes}{ \href{http://colinhowes.com}{\custombold{colinhowes.com}} | 
GitHub:/\href{https://github.com/chowes}{\custombold{chowes}} | LinkedIn:/\href{https://www.linkedin.com/in/colin-howes/}{\custombold{colin-howes}} \\
\href{mailto:chowes@uwaterloo.ca}{chowes@uwaterloo.ca} | 226-979-1031
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{MMath - Computer Science}
\descript{University of Waterloo}
\location{December 2018 \\ GPA: 3.98 \textbullet{} CAV: 93 \%}
\sectionsep

\subsection{MSc - Neuroscience}
\descript{University of Guelph}
\location{December 2016 \\ GPA: 3.98 \textbullet{} CAV: 94 \%}\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming Languages}
C \textbullet{} Java \textbullet{} C++ \textbullet{} Python
\sectionsep

\subsection{Technologies and Tools}
Git \textbullet{} Linux \textbullet{} TensorFlow \textbullet{} Android \\
gRPC \textbullet{} Shell Scripting \textbullet{} \LaTeX
\sectionsep

\subsection{Concepts}
Distributed Systems \textbullet{} Security \\
Networks \textbullet{} Kernel Development \\
Artificial Intelligence \\

\sectionsep
\sectionsep
\subsection{Coursework}
Empirical Performance Evaluation - 91\%\\
Advanced Distributed Systems - 96\%\\
Artificial Intelligence - 89\%\\
Computer Networks - 96\%\\
Computer Security and Privacy - 96\%\\
Research Design and Statistics - 96\%\\
Operating Systems - 91\%\\
Algorithms - 89\%\\
Data Structures 94\%\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{BlackBerry QNX}
\descript{\\Core OS Software Development Student}
\location{Jan 2018 - Present  | Kanata, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Current intern on the kernel development team.
\item Responsible for writing unittests and patches for QNX kernel code and the C standard library.
\end{tightemize}
\sectionsep

\runsubsection{Perception Team Core Member}
\descript{\\WATonomous - SAE AutoDrive Challenge Team}
\location{Sep 2017 - Present  | Waterloo, ON}
\begin{tightemize}
\item Developed and trained an image classifier based on a convolutional neural network capable of classifying traffic signs using Python and TensorFlow.
\item The trained model was capable of rapidly classifying images from 42 classes of traffic signs with 96 \% accuracy.
\end{tightemize}
\sectionsep

\runsubsection{Graduate Research Assistant}
\descript{\\University of Guelph - Department of Computer Science}
\location{Dec 2015 – Dec 2016 | Guelph, ON}
\begin{tightemize}
\item Developed a survey platform backed by PHP and MySQL using AngularJS and Bootstrap at the front end. 
\item Designed in collaboration with a team of public health researchers to facilitate data collection from remote communities.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Analysis of TCP BBR for Data Centres}
\descript{\href{https://github.com/chowes/data-center-bbr.git}{GitHub}}
\begin{tightemize}
\item Assessed throughput and latency performance of TCP BBR as an alternative congestion control algorithm for data centres supporting latency critical distributed applications.
\item Implemented a distributed network performance measurement tool in C++ capable of monitoring and coordinating concurrent connections from 40 nodes on a high speed cluster.
\end{tightemize}
\sectionsep

\runsubsection{W\small{at}\large{FS}}
\descript{\href{https://github.com/chowes/WatFS}{GitHub}}
\begin{tightemize}
\item Fault tolerant remote file system built on top of FUSE, using RPC as a communication mechanism. 
\item WatFS uses batched writes similar to NFSv3, and is capable of sustaining speeds fast enough to stream 4k video over WiFi.
\end{tightemize}
\sectionsep

\runsubsection{Improved Initiative}
\descript{\href{https://github.com/chowes/improved-initiative}{GitHub} | \href{https://play.google.com/store/apps/details?id=me.colinhowes.rollinitiative}{Google Play}}
\begin{tightemize}
\item Developed an Android app to facilitate gameplay management for tabletop roleplaying games like Dungeons and Dragons
\item Over 1000 users and a 4.2 star rating on the Google Play Store
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
